\LARGE \bf Steering a Swarm of Particles\\ Using Global Inputs and Swarm Statistics

### 2017-11-16 2017-tro-SteeringSwarmParticles/SwarmControlJournal.tex
Added bios and pictures.

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{shiva.jpg}}]{Shiva Shahrokhi}(S`14) is a PhD Candidate in the Electrical and Computer Engineering Department at the University of Houston expected to graduate in 2018.

She received the B.S. degree in Computer Engineering from Iran University of Science and Technology,
Tehran, Iran. She is involved in studies of swarm manipulation and control for robotics applications.
These include steering massively under-actuated mobile robotic ensembles, swarm shape control, and machine learning.

\end{IEEEbiography}
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{Lillian.jpg}}]{Lillian Lin}(S`14) is currently pursuing a B.S. degree in Electrical Engineering from the University of Houston, Houston, Texas, and is expected to graduate in 2018.
She is currently the president of the student IEEE branch on campus. She works as an undergraduate researcher at the University of Houston at the Robotics Swarm Control lab. Her main research interests include robotic control systems.

\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{chris_portrait.jpg}}]{Chris Ertel} Chris Ertel received his B.S. in mechanical engineering from Rice University in 2010, and has since worked in industry and startups developing games, computer-aided design applications, medical telemetry systems, and other software.
Since 2013 he's collaborated with Dr. Becker on SwarmControl.net and related projects at the University of Houston Robotic Swarm Control Lab and the Rice Multi-Robot Systems Lab.

\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mable.jpg}}]{Mable Wan} Mable Wan received a B.S. degree in electrical and computer engineering and a B.B.A. in entrepreneurship from the University of Houston in 2017.
Since May 2017, she has been working with Northrop Grumman Corporation in Baltimore, MD as a software engineer.
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{DrB.jpg}}]{Aaron T. Becker}(M`06) received M.S. and PhD degrees in electrical and computer engineering from the University of Illinois at Urbana-Champaign, in 2008 and 2012. He was a post doctoral research scholar at the Multi-Robot Systems Lab at Rice University and a post doctoral research fellow at Boston Children's Hospital, Harvard Medical School, before joining the Electrical and Computer Engineering Department at the University of Houston as an Assistant Professor in 2014. He won the best paper at IROS 2013 and received the NSF CAREER award in 2016. He is active in developing control laws and algorithms for robot swarms.

\end{IEEEbiography}
